### 2020-04-29 rR.tex
new fig

% Created by tikzDevice version 0.12.3 on 2020-04-14 17:43:43
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31,247.65) --
	( 30.56,248.50) --
	( 33.80,249.37) --
	( 37.04,250.25) --
	( 40.29,251.16) --
	( 43.53,252.09) --
	( 46.78,253.03) --
	( 50.02,254.00) --
	( 53.26,254.98) --
	( 56.51,255.98) --
	( 59.75,257.00) --
	( 63.00,258.04) --
	( 66.24,259.10) --
	( 69.48,260.18) --
	( 72.73,261.28) --
	( 75.97,262.40) --
	( 79.22,263.54) --
	( 82.46,264.70) --
	( 85.70,265.88) --
	( 88.95,267.07) --
	( 92.19,268.29) --
	( 95.43,269.52) --
	( 98.68,270.77) --
	(101.92,272.04) --
	(105.17,273.33) --
	(108.41,274.63) --
	(111.65,275.96) --
	(114.90,277.31) --
	(118.14,278.69) --
	(121.39,280.08) --
	(124.63,281.50) --
	(127.87,282.94) --
	(131.12,284.39) --
	(134.36,285.86) --
	(137.61,287.35) --
	(140.85,288.87) --
	(144.09,290.41) --
	(147.34,291.97) --
	(150.58,293.56) --
	(153.82,295.18) --
	(157.07,296.83) --
	(160.31,298.49) --
	(163.56,300.18) --
	(166.80,301.88) --
	(170.04,303.60) --
	(173.29,305.35) --
	(176.53,307.13) --
	(179.78,308.93) --
	(183.02,310.77) --
	(186.26,312.64) --
	(189.51,314.55) --
	(192.75,316.48) --
	(196.00,318.44) --
	(199.24,320.43) --
	(202.48,322.45) --
	(205.73,324.49) --
	(208.97,326.57) --
	(212.21,328.67) --
	(215.46,330.81) --
	(218.70,332.98) --
	(221.95,335.19) --
	(225.19,337.43) --
	(228.43,339.70) --
	(231.68,342.00) --
	(234.92,344.33) --
	(238.17,346.69) --
	(241.41,349.09) --
	(244.65,351.51) --
	(247.90,353.96) --
	(251.14,356.45) --
	(254.39,358.97) --
	(257.63,361.51) --
	(260.87,364.10) --
	(264.12,366.71) --
	(267.36,369.35) --
	(270.60,372.03) --
	(273.85,374.73) --
	(277.09,377.47) --
	(280.34,380.24) --
	(283.58,383.04);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.62) --
	( 30.56,248.48) --
	( 33.80,249.35) --
	( 37.04,250.25) --
	( 40.29,251.16) --
	( 43.53,252.10) --
	( 46.78,253.05) --
	( 50.02,254.02) --
	( 53.26,255.01) --
	( 56.51,256.02) --
	( 59.75,257.05) --
	( 63.00,258.09) --
	( 66.24,259.16) --
	( 69.48,260.24) --
	( 72.73,261.35) --
	( 75.97,262.47) --
	( 79.22,263.61) --
	( 82.46,264.77) --
	( 85.70,265.96) --
	( 88.95,267.16) --
	( 92.19,268.38) --
	( 95.43,269.61) --
	( 98.68,270.86) --
	(101.92,272.13) --
	(105.17,273.42) --
	(108.41,274.73) --
	(111.65,276.06) --
	(114.90,277.41) --
	(118.14,278.78) --
	(121.39,280.18) --
	(124.63,281.60) --
	(127.87,283.02) --
	(131.12,284.47) --
	(134.36,285.93) --
	(137.61,287.42) --
	(140.85,288.92) --
	(144.09,290.45) --
	(147.34,292.01) --
	(150.58,293.59) --
	(153.82,295.21) --
	(157.07,296.85) --
	(160.31,298.51) --
	(163.56,300.20) --
	(166.80,301.90) --
	(170.04,303.62) --
	(173.29,305.37) --
	(176.53,307.14) --
	(179.78,308.95) --
	(183.02,310.78) --
	(186.26,312.65) --
	(189.51,314.55) --
	(192.75,316.49) --
	(196.00,318.45) --
	(199.24,320.44) --
	(202.48,322.45) --
	(205.73,324.49) --
	(208.97,326.57) --
	(212.21,328.67) --
	(215.46,330.81) --
	(218.70,332.98) --
	(221.95,335.19) --
	(225.19,337.43) --
	(228.43,339.70) --
	(231.68,342.01) --
	(234.92,344.34) --
	(238.17,346.71) --
	(241.41,349.11) --
	(244.65,351.53) --
	(247.90,353.99) --
	(251.14,356.48) --
	(254.39,359.01) --
	(257.63,361.56) --
	(260.87,364.15) --
	(264.12,366.77) --
	(267.36,369.42) --
	(270.60,372.10) --
	(273.85,374.82) --
	(277.09,377.56) --
	(280.34,380.34) --
	(283.58,383.15);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31,247.61) --
	( 30.56,248.47) --
	( 33.80,249.35) --
	( 37.04,250.24) --
	( 40.29,251.16) --
	( 43.53,252.10) --
	( 46.78,253.05) --
	( 50.02,254.02) --
	( 53.26,255.02) --
	( 56.51,256.03) --
	( 59.75,257.06) --
	( 63.00,258.10) --
	( 66.24,259.17) --
	( 69.48,260.26) --
	( 72.73,261.36) --
	( 75.97,262.48) --
	( 79.22,263.63) --
	( 82.46,264.79) --
	( 85.70,265.97) --
	( 88.95,267.17) --
	( 92.19,268.39) --
	( 95.43,269.63) --
	( 98.68,270.88) --
	(101.92,272.15) --
	(105.17,273.44) --
	(108.41,274.75) --
	(111.65,276.08) --
	(114.90,277.43) --
	(118.14,278.80) --
	(121.39,280.20) --
	(124.63,281.61) --
	(127.87,283.04) --
	(131.12,284.48) --
	(134.36,285.94) --
	(137.61,287.42) --
	(140.85,288.92) --
	(144.09,290.45) --
	(147.34,292.00) --
	(150.58,293.58) --
	(153.82,295.19) --
	(157.07,296.84) --
	(160.31,298.49) --
	(163.56,300.17) --
	(166.80,301.87) --
	(170.04,303.59) --
	(173.29,305.33) --
	(176.53,307.10) --
	(179.78,308.90) --
	(183.02,310.73) --
	(186.26,312.60) --
	(189.51,314.50) --
	(192.75,316.44) --
	(196.00,318.40) --
	(199.24,320.39) --
	(202.48,322.40) --
	(205.73,324.45) --
	(208.97,326.53) --
	(212.21,328.63) --
	(215.46,330.78) --
	(218.70,332.95) --
	(221.95,335.17) --
	(225.19,337.42) --
	(228.43,339.70) --
	(231.68,342.01) --
	(234.92,344.36) --
	(238.17,346.74) --
	(241.41,349.14) --
	(244.65,351.58) --
	(247.90,354.06) --
	(251.14,356.56) --
	(254.39,359.10) --
	(257.63,361.67) --
	(260.87,364.27) --
	(264.12,366.91) --
	(267.36,369.58) --
	(270.60,372.28) --
	(273.85,375.01) --
	(277.09,377.78) --
	(280.34,380.58) --
	(283.58,383.41);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31,247.60) --
	( 30.56,248.46) --
	( 33.80,249.34) --
	( 37.04,250.24) --
	( 40.29,251.16) --
	( 43.53,252.09) --
	( 46.78,253.05) --
	( 50.02,254.02) --
	( 53.26,255.02) --
	( 56.51,256.03) --
	( 59.75,257.06) --
	( 63.00,258.11) --
	( 66.24,259.18) --
	( 69.48,260.26) --
	( 72.73,261.37) --
	( 75.97,262.49) --
	( 79.22,263.64) --
	( 82.46,264.80) --
	( 85.70,265.98) --
	( 88.95,267.19) --
	( 92.19,268.40) --
	( 95.43,269.64) --
	( 98.68,270.89) --
	(101.92,272.16) --
	(105.17,273.45) --
	(108.41,274.76) --
	(111.65,276.09) --
	(114.90,277.44) --
	(118.14,278.81) --
	(121.39,280.21) --
	(124.63,281.62) --
	(127.87,283.04) --
	(131.12,284.48) --
	(134.36,285.94) --
	(137.61,287.42) --
	(140.85,288.92) --
	(144.09,290.44) --
	(147.34,291.99) --
	(150.58,293.57) --
	(153.82,295.18) --
	(157.07,296.82) --
	(160.31,298.48) --
	(163.56,300.15) --
	(166.80,301.85) --
	(170.04,303.56) --
	(173.29,305.30) --
	(176.53,307.07) --
	(179.78,308.87) --
	(183.02,310.70) --
	(186.26,312.56) --
	(189.51,314.47) --
	(192.75,316.41) --
	(196.00,318.37) --
	(199.24,320.36) --
	(202.48,322.38) --
	(205.73,324.43) --
	(208.97,326.51) --
	(212.21,328.63) --
	(215.46,330.77) --
	(218.70,332.96) --
	(221.95,335.18) --
	(225.19,337.45) --
	(228.43,339.74) --
	(231.68,342.07) --
	(234.92,344.42) --
	(238.17,346.82) --
	(241.41,349.24) --
	(244.65,351.70) --
	(247.90,354.18) --
	(251.14,356.71) --
	(254.39,359.26) --
	(257.63,361.85) --
	(260.87,364.48) --
	(264.12,367.14) --
	(267.36,369.83) --
	(270.60,372.55) --
	(273.85,375.31) --
	(277.09,378.11) --
	(280.34,380.93) --
	(283.58,383.79);
\definecolor{fillColor}{RGB}{230,159,0}

@@

\path[fill=fillColor] ( 35.86,253.77) --
	( 39.22,247.94) --
	( 32.49,247.94) --
	cycle;

\path[fill=fillColor] ( 44.40,256.26) --
	( 47.76,250.43) --
	( 41.03,250.43) --
	cycle;

\path[fill=fillColor] ( 52.94,258.86) --
	( 56.30,253.03) --
	( 49.58,253.03) --
	cycle;

@@

\path[fill=fillColor] ( 70.02,264.40) --
	( 73.39,258.57) --
	( 66.66,258.57) --
	cycle;

\path[fill=fillColor] ( 78.57,267.34) --
	( 81.93,261.52) --
	( 75.20,261.52) --
	cycle;

\path[fill=fillColor] ( 87.11,270.42) --
	( 90.47,264.59) --
	( 83.75,264.59) --
	cycle;

@@

\path[fill=fillColor] (104.19,276.97) --
	(107.56,271.14) --
	(100.83,271.14) --
	cycle;

\path[fill=fillColor] (112.74,280.44) --
	(116.10,274.61) --
	(109.37,274.61) --
	cycle;

\path[fill=fillColor] (121.28,284.03) --
	(124.64,278.20) --
	(117.91,278.20) --
	cycle;

@@

\path[fill=fillColor] (138.36,291.67) --
	(141.73,285.84) --
	(135.00,285.84) --
	cycle;

\path[fill=fillColor] (146.90,295.72) --
	(150.27,289.89) --
	(143.54,289.89) --
	cycle;

\path[fill=fillColor] (155.45,299.91) --
	(158.81,294.09) --
	(152.08,294.09) --
	cycle;

@@

\path[fill=fillColor] (172.53,308.81) --
	(175.89,302.98) --
	(169.17,302.98) --
	cycle;

\path[fill=fillColor] (181.07,313.60) --
	(184.44,307.77) --
	(177.71,307.77) --
	cycle;

\path[fill=fillColor] (189.62,318.53) --
	(192.98,312.70) --
	(186.25,312.70) --
	cycle;

@@

\path[fill=fillColor] (206.70,328.95) --
	(210.06,323.12) --
	(203.34,323.12) --
	cycle;

\path[fill=fillColor] (215.24,334.48) --
	(218.61,328.65) --
	(211.88,328.65) --
	cycle;

\path[fill=fillColor] (223.78,340.26) --
	(227.15,334.44) --
	(220.42,334.44) --
	cycle;

@@

\path[fill=fillColor] (240.87,352.35) --
	(244.23,346.52) --
	(237.51,346.52) --
	cycle;

\path[fill=fillColor] (249.41,358.83) --
	(252.77,353.01) --
	(246.05,353.01) --
	cycle;

\path[fill=fillColor] (257.95,365.61) --
	(261.32,359.79) --
	(254.59,359.79) --
	cycle;

\path[fill=fillColor] (266.50,372.59) --
	(269.86,366.77) --
	(263.13,366.77) --
	cycle;

\path[fill=fillColor] (275.04,379.74) --
	(278.40,373.92) --
	(271.67,373.92) --
	cycle;

\path[fill=fillColor] (283.58,387.27) --
	(286.94,381.45) --
	(280.22,381.45) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

\path[fill=fillColor] ( 24.82,245.00) --
	( 29.81,245.00) --
	( 29.81,249.99) --
	( 24.82,249.99) --
	cycle;

@@

\path[fill=fillColor] ( 41.90,249.87) --
	( 46.90,249.87) --
	( 46.90,254.87) --
	( 41.90,254.87) --
	cycle;

\path[fill=fillColor] ( 50.44,252.48) --
	( 55.44,252.48) --
	( 55.44,257.47) --
	( 50.44,257.47) --
	cycle;

\path[fill=fillColor] ( 58.98,255.19) --
	( 63.98,255.19) --
	( 63.98,260.19) --
	( 58.98,260.19) --
	cycle;

@@

\path[fill=fillColor] ( 76.07,260.97) --
	( 81.06,260.97) --
	( 81.06,265.96) --
	( 76.07,265.96) --
	cycle;

\path[fill=fillColor] ( 84.61,264.05) --
	( 89.61,264.05) --
	( 89.61,269.04) --
	( 84.61,269.04) --
	cycle;

\path[fill=fillColor] ( 93.15,267.26) --
	( 98.15,267.26) --
	( 98.15,272.26) --
	( 93.15,272.26) --
	cycle;

@@

\path[fill=fillColor] (110.24,274.08) --
	(115.23,274.08) --
	(115.23,279.07) --
	(110.24,279.07) --
	cycle;

\path[fill=fillColor] (118.78,277.67) --
	(123.78,277.67) --
	(123.78,282.67) --
	(118.78,282.67) --
	cycle;

\path[fill=fillColor] (127.32,281.41) --
	(132.32,281.41) --
	(132.32,286.41) --
	(127.32,286.41) --
	cycle;

@@

\path[fill=fillColor] (144.41,289.34) --
	(149.40,289.34) --
	(149.40,294.33) --
	(144.41,294.33) --
	cycle;

\path[fill=fillColor] (152.95,293.52) --
	(157.94,293.52) --
	(157.94,298.51) --
	(152.95,298.51) --
	cycle;

\path[fill=fillColor] (161.49,297.83) --
	(166.49,297.83) --
	(166.49,302.82) --
	(161.49,302.82) --
	cycle;

@@

\path[fill=fillColor] (178.58,307.19) --
	(183.57,307.19) --
	(183.57,312.18) --
	(178.58,312.18) --
	cycle;

\path[fill=fillColor] (187.12,312.12) --
	(192.11,312.12) --
	(192.11,317.12) --
	(187.12,317.12) --
	cycle;

\path[fill=fillColor] (195.66,317.22) --
	(200.66,317.22) --
	(200.66,322.21) --
	(195.66,322.21) --
	cycle;

@@

\path[fill=fillColor] (212.74,328.07) --
	(217.74,328.07) --
	(217.74,333.06) --
	(212.74,333.06) --
	cycle;

\path[fill=fillColor] (221.29,333.88) --
	(226.28,333.88) --
	(226.28,338.88) --
	(221.29,338.88) --
	cycle;

\path[fill=fillColor] (229.83,339.76) --
	(234.82,339.76) --
	(234.82,344.75) --
	(229.83,344.75) --
	cycle;

@@

\path[fill=fillColor] (246.91,352.51) --
	(251.91,352.51) --
	(251.91,357.51) --
	(246.91,357.51) --
	cycle;

\path[fill=fillColor] (255.46,359.41) --
	(260.45,359.41) --
	(260.45,364.40) --
	(255.46,364.40) --
	cycle;

\path[fill=fillColor] (264.00,366.42) --
	(268.99,366.42) --
	(268.99,371.41) --
	(264.00,371.41) --
	cycle;

@@

\path[fill=fillColor] (281.08,381.15) --
	(286.08,381.15) --
	(286.08,386.15) --
	(281.08,386.15) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 23.78,247.50) -- ( 30.85,247.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 27.31,243.96) -- ( 27.31,251.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.32,249.88) -- ( 39.39,249.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.86,246.35) -- ( 35.86,253.41);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.41,254.97) -- ( 56.47,254.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.94,251.44) -- ( 52.94,258.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.95,257.69) -- ( 65.01,257.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48,254.15) -- ( 61.48,261.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49,260.51) -- ( 73.56,260.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02,256.98) -- ( 70.02,264.05);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,266.55) -- ( 90.64,266.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,263.02) -- ( 87.11,270.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,269.78) -- ( 99.18,269.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,266.24) -- ( 95.65,273.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,273.13) -- (107.73,273.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,269.60) -- (104.19,276.66);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,280.19) -- (124.81,280.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,276.66) -- (121.28,283.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.92) -- (133.35,283.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,280.39) -- (129.82,287.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,287.81) -- (141.89,287.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,284.28) -- (138.36,291.35);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.91,296.01) -- (158.98,296.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.45,292.47) -- (155.45,299.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,300.29) -- (167.52,300.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,296.75) -- (163.99,303.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,304.81) -- (176.06,304.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.27) -- (172.53,308.34);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.08,314.61) -- (193.15,314.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,311.07) -- (189.62,318.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,319.70) -- (201.69,319.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,316.17) -- (198.16,323.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,324.99) -- (210.23,324.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,321.46) -- (206.70,328.52);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.25,336.41) -- (227.32,336.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.78,332.88) -- (223.78,339.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,342.22) -- (235.86,342.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,338.69) -- (232.33,345.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.34,348.37) -- (244.40,348.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.87,344.84) -- (240.87,351.90);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,362.17) -- (261.49,362.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,358.64) -- (257.95,365.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.96,369.21) -- (270.03,369.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (266.50,365.68) -- (266.50,372.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.51,376.31) -- (278.57,376.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.04,372.78) -- (275.04,379.84);

@@

\path[fill=fillColor] ( 27.31,247.50) circle (  2.50);

\path[fill=fillColor] ( 35.86,249.88) circle (  2.50);

\path[fill=fillColor] ( 44.40,252.37) circle (  2.50);

\path[fill=fillColor] ( 52.94,254.94) circle (  2.50);

\path[fill=fillColor] ( 61.48,257.68) circle (  2.50);

\path[fill=fillColor] ( 70.02,260.47) circle (  2.50);

\path[fill=fillColor] ( 78.57,263.41) circle (  2.50);

@@

\path[fill=fillColor] ( 95.65,269.65) circle (  2.50);

\path[fill=fillColor] (104.19,273.00) circle (  2.50);

\path[fill=fillColor] (112.74,276.42) circle (  2.50);

\path[fill=fillColor] (121.28,279.99) circle (  2.50);

\path[fill=fillColor] (129.82,283.76) circle (  2.50);

\path[fill=fillColor] (138.36,287.74) circle (  2.50);

\path[fill=fillColor] (146.90,291.70) circle (  2.50);

\path[fill=fillColor] (155.45,296.03) circle (  2.50);

\path[fill=fillColor] (163.99,300.46) circle (  2.50);

\path[fill=fillColor] (172.53,304.98) circle (  2.50);

\path[fill=fillColor] (181.07,309.73) circle (  2.50);

\path[fill=fillColor] (189.62,314.62) circle (  2.50);

\path[fill=fillColor] (198.16,319.79) circle (  2.50);

\path[fill=fillColor] (206.70,324.93) circle (  2.50);

\path[fill=fillColor] (215.24,330.66) circle (  2.50);

\path[fill=fillColor] (223.78,336.18) circle (  2.50);

\path[fill=fillColor] (232.33,342.09) circle (  2.50);

\path[fill=fillColor] (240.87,348.75) circle (  2.50);

\path[fill=fillColor] (249.41,355.20) circle (  2.50);

\path[fill=fillColor] (257.95,361.58) circle (  2.50);

\path[fill=fillColor] (266.50,368.62) circle (  2.50);

\path[fill=fillColor] (275.04,375.76) circle (  2.50);

>>>>

% Created by tikzDevice version 0.12.3 on 2020-04-29 03:55:17
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 52.94,254.97) --
	( 55.54,255.77) --
	( 58.13,256.58) --
	( 60.73,257.40) --
	( 63.32,258.23) --
	( 65.92,259.08) --
	( 68.51,259.94) --
	( 71.11,260.81) --
	( 73.70,261.69) --
	( 76.30,262.59) --
	( 78.89,263.49) --
	( 81.49,264.42) --
	( 84.08,265.35) --
	( 86.68,266.30) --
	( 89.27,267.26) --
	( 91.87,268.23) --
	( 94.46,269.21) --
	( 97.06,270.20) --
	( 99.65,271.21) --
	(102.25,272.23) --
	(104.84,273.26) --
	(107.44,274.30) --
	(110.03,275.36) --
	(112.63,276.43) --
	(115.22,277.51) --
	(117.82,278.61) --
	(120.41,279.72) --
	(123.01,280.84) --
	(125.60,281.98) --
	(128.20,283.13) --
	(130.79,284.29) --
	(133.39,285.46) --
	(135.98,286.65) --
	(138.58,287.85) --
	(141.17,289.07) --
	(143.77,290.31) --
	(146.36,291.55) --
	(148.96,292.82) --
	(151.55,294.10) --
	(154.15,295.40) --
	(156.74,296.71) --
	(159.34,298.04) --
	(161.93,299.39) --
	(164.53,300.75) --
	(167.12,302.12) --
	(169.72,303.51) --
	(172.31,304.92) --
	(174.91,306.34) --
	(177.51,307.78) --
	(180.10,309.24) --
	(182.70,310.71) --
	(185.29,312.21) --
	(187.89,313.72) --
	(190.48,315.26) --
	(193.08,316.81) --
	(195.67,318.38) --
	(198.27,319.97) --
	(200.86,321.57) --
	(203.46,323.20) --
	(206.05,324.84) --
	(208.65,326.51) --
	(211.24,328.19) --
	(213.84,329.89) --
	(216.43,331.62) --
	(219.03,333.36) --
	(221.62,335.12) --
	(224.22,336.91) --
	(226.81,338.72) --
	(229.41,340.54) --
	(232.00,342.39) --
	(234.60,344.25) --
	(237.19,346.14) --
	(239.79,348.04) --
	(242.38,349.97) --
	(244.98,351.91) --
	(247.57,353.87) --
	(250.17,355.85) --
	(252.76,357.85) --
	(255.36,359.88) --
	(257.95,361.92);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.52) --
	( 30.34,248.34) --
	( 33.37,249.16) --
	( 36.40,250.01) --
	( 39.42,250.87) --
	( 42.45,251.74) --
	( 45.48,252.64) --
	( 48.51,253.54) --
	( 51.53,254.47) --
	( 54.56,255.41) --
	( 57.59,256.36) --
	( 60.62,257.34) --
	( 63.64,258.32) --
	( 66.67,259.33) --
	( 69.70,260.35) --
	( 72.73,261.38) --
	( 75.76,262.43) --
	( 78.78,263.50) --
	( 81.81,264.58) --
	( 84.84,265.68) --
	( 87.87,266.80) --
	( 90.89,267.93) --
	( 93.92,269.08) --
	( 96.95,270.25) --
	( 99.98,271.42) --
	(103.00,272.61) --
	(106.03,273.81) --
	(109.06,275.03) --
	(112.09,276.26) --
	(115.11,277.51) --
	(118.14,278.77) --
	(121.17,280.06) --
	(124.20,281.37) --
	(127.22,282.71) --
	(130.25,284.06) --
	(133.28,285.44) --
	(136.31,286.83) --
	(139.34,288.23) --
	(142.36,289.64) --
	(145.39,291.08) --
	(148.42,292.53) --
	(151.45,294.01) --
	(154.47,295.51) --
	(157.50,297.03) --
	(160.53,298.59) --
	(163.56,300.17) --
	(166.58,301.77) --
	(169.61,303.39) --
	(172.64,305.02) --
	(175.67,306.68) --
	(178.69,308.35) --
	(181.72,310.04) --
	(184.75,311.76) --
	(187.78,313.51) --
	(190.80,315.28) --
	(193.83,317.09) --
	(196.86,318.92) --
	(199.89,320.80) --
	(202.92,322.69) --
	(205.94,324.62) --
	(208.97,326.56) --
	(212.00,328.54) --
	(215.03,330.54) --
	(218.05,332.56) --
	(221.08,334.62) --
	(224.11,336.70) --
	(227.14,338.80) --
	(230.16,340.94) --
	(233.19,343.10) --
	(236.22,345.29) --
	(239.25,347.50) --
	(242.27,349.75) --
	(245.30,352.02) --
	(248.33,354.31) --
	(251.36,356.63) --
	(254.39,358.98) --
	(257.41,361.36) --
	(260.44,363.76) --
	(263.47,366.19) --
	(266.50,368.65);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 35.86,249.91) --
	( 38.88,250.76) --
	( 41.91,251.62) --
	( 44.94,252.51) --
	( 47.97,253.41) --
	( 50.99,254.32) --
	( 54.02,255.26) --
	( 57.05,256.21) --
	( 60.08,257.17) --
	( 63.10,258.15) --
	( 66.13,259.15) --
	( 69.16,260.17) --
	( 72.19,261.20) --
	( 75.21,262.25) --
	( 78.24,263.31) --
	( 81.27,264.39) --
	( 84.30,265.48) --
	( 87.33,266.60) --
	( 90.35,267.72) --
	( 93.38,268.87) --
	( 96.41,270.03) --
	( 99.44,271.21) --
	(102.46,272.41) --
	(105.49,273.62) --
	(108.52,274.84) --
	(111.55,276.08) --
	(114.57,277.32) --
	(117.60,278.59) --
	(120.63,279.86) --
	(123.66,281.16) --
	(126.68,282.48) --
	(129.71,283.81) --
	(132.74,285.17) --
	(135.77,286.56) --
	(138.79,287.97) --
	(141.82,289.39) --
	(144.85,290.83) --
	(147.88,292.29) --
	(150.91,293.76) --
	(153.93,295.24) --
	(156.96,296.75) --
	(159.99,298.28) --
	(163.02,299.84) --
	(166.04,301.42) --
	(169.07,303.03) --
	(172.10,304.67) --
	(175.13,306.33) --
	(178.15,308.01) --
	(181.18,309.70) --
	(184.21,311.42) --
	(187.24,313.15) --
	(190.26,314.90) --
	(193.29,316.68) --
	(196.32,318.49) --
	(199.35,320.33) --
	(202.37,322.21) --
	(205.40,324.12) --
	(208.43,326.06) --
	(211.46,328.03) --
	(214.49,330.03) --
	(217.51,332.06) --
	(220.54,334.11) --
	(223.57,336.19) --
	(226.60,338.30) --
	(229.62,340.44) --
	(232.65,342.61) --
	(235.68,344.80) --
	(238.71,347.02) --
	(241.73,349.28) --
	(244.76,351.56) --
	(247.79,353.87) --
	(250.82,356.21) --
	(253.84,358.58) --
	(256.87,360.97) --
	(259.90,363.40) --
	(262.93,365.85) --
	(265.95,368.33) --
	(268.98,370.84) --
	(272.01,373.38) --
	(275.04,375.95);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.40,252.39) --
	( 47.43,253.28) --
	( 50.45,254.18) --
	( 53.48,255.11) --
	( 56.51,256.05) --
	( 59.54,257.00) --
	( 62.56,257.98) --
	( 65.59,258.97) --
	( 68.62,259.97) --
	( 71.65,261.00) --
	( 74.67,262.04) --
	( 77.70,263.10) --
	( 80.73,264.17) --
	( 83.76,265.26) --
	( 86.78,266.37) --
	( 89.81,267.49) --
	( 92.84,268.63) --
	( 95.87,269.79) --
	( 98.89,270.97) --
	(101.92,272.16) --
	(104.95,273.37) --
	(107.98,274.60) --
	(111.01,275.84) --
	(114.03,277.11) --
	(117.06,278.38) --
	(120.09,279.67) --
	(123.12,280.97) --
	(126.14,282.28) --
	(129.17,283.61) --
	(132.20,284.96) --
	(135.23,286.33) --
	(138.25,287.72) --
	(141.28,289.14) --
	(144.31,290.58) --
	(147.34,292.05) --
	(150.36,293.53) --
	(153.39,295.03) --
	(156.42,296.54) --
	(159.45,298.06) --
	(162.48,299.61) --
	(165.50,301.18) --
	(168.53,302.77) --
	(171.56,304.38) --
	(174.59,306.03) --
	(177.61,307.70) --
	(180.64,309.41) --
	(183.67,311.14) --
	(186.70,312.89) --
	(189.72,314.66) --
	(192.75,316.45) --
	(195.78,318.25) --
	(198.81,320.09) --
	(201.83,321.94) --
	(204.86,323.83) --
	(207.89,325.76) --
	(210.92,327.71) --
	(213.94,329.71) --
	(216.97,331.74) --
	(220.00,333.80) --
	(223.03,335.89) --
	(226.06,338.01) --
	(229.08,340.16) --
	(232.11,342.33) --
	(235.14,344.54) --
	(238.17,346.77) --
	(241.19,349.04) --
	(244.22,351.34) --
	(247.25,353.67) --
	(250.28,356.02) --
	(253.30,358.41) --
	(256.33,360.83) --
	(259.36,363.28) --
	(262.39,365.76) --
	(265.41,368.27) --
	(268.44,370.81) --
	(271.47,373.38) --
	(274.50,375.98) --
	(277.52,378.61) --
	(280.55,381.26) --
	(283.58,383.95);
\definecolor{fillColor}{RGB}{230,159,0}

@@

@@

@@

@@

@@

@@

@@

\path[fill=fillColor] (266.50,372.59) --
	(269.86,366.77) --
	(263.13,366.77) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

\path[fill=fillColor] ( 52.94,254.96) circle (  2.50);

@@

\path[fill=fillColor] (121.28,280.09) circle (  2.50);

\path[fill=fillColor] (155.45,296.05) circle (  2.50);

\path[fill=fillColor] (189.62,314.74) circle (  2.50);

\path[fill=fillColor] (223.78,336.55) circle (  2.50);

\path[fill=fillColor] (257.95,361.93) circle (  2.50);
\definecolor{drawColor}{gray}{0.20}
